Vulnerability Analysis of Container Images in Neuroimaging

### 2020-06-30 paper.tex
added abstract

\begin{abstract}
	\tristan{Abstract goes here}
\end{abstract}

@@

% Container images, our study
This study is a vulnerability analysis of container images used in HPC
clusters. Container images contain complete operating-system distributions,
including the data analysis software and its required dependencies.
Images are rarely updated, as they are often built once
for the entire duration of an analysis, to avoid results perturbations
coming from software updates~\cite{gronenschild, glatard2015}. Images also
commonly include more dependencies than required by a specific analysis, to 
enable reusability across experiments.

@@

\textit{RQ1: What is the current amount of known vulnerabilities in
container images deployed on HPC clusters?} Vulnerabilities are possible
attack vectors that may seriously compromise the security of HPC clusters
and the integrity of user data. We report vulnerability analyses produced
by four popular image scanning tools, Anchore, Vuls, Clair and Stools.

@@

We answer these questions taking the particular example of neuroimaging, a
domain that has entered the Big Data era as many other
ones~\cite{vanhorn-toga}. We focus on the analysis of container images
present in BIDS apps~\cite{xxx} and Boutiques~\cite{xxx}, two containerized
application frameworks commonly used in neuroimaging.

@@

We find a total of 20,050 vulnerabilities in BIDS apps and Boutiques images.
It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 by Clair, and 325 by Vuls.

@@

\section{Conclusions}

As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
so many are critical vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
already reached end-of-life and are
no longer getting updates. Furthermore, the minimization of images is a time consuming process. As we have to run
the pipeline to get Reprozip trace that can take up to several hours. Also, the user should have proper knowledge
of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
in the images having Python version 2.7.3 or greater, or 3.3 or greater. Above all, there is no guarantee that
the commands that you ran to get Reprozip trace covered the whole program, maybe it runs a particular
branch of the program. So there should be some kind of coverage measurement.
Besides this, as scanners report vulnerabilities according to the versions of the installed packages,
they are likely to miss packages that are not installed using package manager. 
Therefore, we suggest some particular rules that can be
followed to keep container images safe.
\newline 1. Update packages regularly.
\newline 2. Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc).
\newline 3. Choose your base OS image wisely.
\newline 4. Run image scanning tools in CI scripts. For instance Anchore.
\newline 5. Protect your GitHub/DockerHub credentials because if automated builds is set up
in Docker Hub, it can automatically build images from external repositories, for instance GitHub.
\newline 6. Minimize dependencies.
\newline 7. Avoid static linking because it obfuscates vulnerability scanning.
\newline 8. Use the package manager to facilitate vulnerability detection.
\newline 9. Use OS releases that have LTS support.
\newline 10. Sign your images. Docker Content Trust (DCT) provides ability to digitally sign
images to verify the integrity of the images.

\section{Summary and Future Work}

>>>>

\begin{abstract}

Today, containers, which provide operating system level virtualization, are
popular. Correspondingly, they are widely used for scientific data analyses on 
High Performance Computing (HPC) clusters. However, the security of containers
still remains the concerning issue. Here, we focus on the security of container
images in particular. Container images are often built for the entire
duration of an analysis, so scientific researchers do not prefer to update
them. Consequently, their chances of containing vulnerabilities increases.  
In this study, we analyze vulnerabilities in container images used in 
HPC clusters.
We conduct two different
experiments, image update and image shrinking, to report the effect 
on the number of vulnerabilities.

\end{abstract}

@@

% Container images, our study
This study is a vulnerability analysis of container images used in HPC
clusters. Container images contain complete operating-system distributions,
including the data analysis software and its required dependencies.
Images are rarely updated, as they are often built once
for the entire duration of an analysis, to avoid results perturbations
coming from software updates~\cite{gronenschild2012effects, glatard2015reproducibility}. Images also
commonly include more dependencies than required by a specific analysis, to 
enable reusability across experiments.

@@

\textit{RQ1: What is the current amount of known vulnerabilities in
container images deployed on HPC clusters?} Vulnerabilities are possible
attack vectors that may seriously compromise the security of HPC clusters
and the integrity of user data. We report vulnerability analyses produced
by four popular image scanning tools, Anchore, Vuls, Clair-scanner and Stools.

@@

We answer these questions taking the particular example of neuroimaging, a
domain that has entered the Big Data era as many other
ones~\cite{van2014human}. We focus on the analysis of container images
present in BIDS apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}, two containerized
application frameworks commonly used in neuroimaging.

@@

We find a total of 20,050 vulnerabilities in BIDS apps and Boutiques images.
It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 by Clair-scanner, and 325 by Vuls.

@@

As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
so many are high vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
already reached end-of-life and are
no longer getting updates. Furthermore, the minimization of images is a time consuming process. As we have to run
the pipeline to get Reprozip trace that can take up to several hours. Also, the user should have proper knowledge
of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
in the images having Python version 2.7.3 or greater, or 3.3 or greater. Above all, there is no guarantee that
the commands that you ran to get Reprozip trace covered the whole program, maybe it runs a particular
branch of the program. So there should be some kind of coverage measurement.
Besides this, as scanners report vulnerabilities according to the versions of the installed packages,
they are likely to miss packages that are not installed using package manager. 
Therefore, we suggest some particular rules that can be
followed to keep container images safe.
\newline 1. Update packages regularly.
\newline 2. Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc).
\newline 3. Choose your base OS image wisely.
\newline 4. Run image scanning tools in CI scripts. For instance Anchore.
\newline 5. Protect your GitHub/DockerHub credentials because if automated builds is set up
in Docker Hub, it can automatically build images from external repositories, for instance GitHub.
\newline 6. Minimize dependencies.
\newline 7. Avoid static linking because it obfuscates vulnerability scanning.
\newline 8. Use the package manager to facilitate vulnerability detection.
\newline 9. Use OS releases that have LTS support.
\newline 10. Sign your images. Docker Content Trust (DCT) provides ability to digitally sign
images to verify the integrity of the images.

\section{Conclusions and Future Work}
